%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://wilfreddenton.com/}{\Large Wilfred Denton}} & Email : \href{mailto:dentonw3@gmail.com}{dentonw3@gmail.com}\\
  \href{https://github.com/wilfreddenton}{https://github.com/wilfreddenton} & Mobile : +1-614-779-4255 \\
\end{tabular*}

%-----------BLERB---------------------
\section{About}
	{Curious, problem solving, full-stack software engineer currently employed at Symbiont. Looking for work in the blockchain/P2P field. Enjoys working with people and can be both a contributing member of a group as well as an effective leader. Can learn and understand new concepts efficiently and apply them when necessary.}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Symbiont}{New York, NY}
      {Software Engineer}{Aug 2017 - Present}
      \resumeItemListStart
        \resumeItem{Smart Contract Language}
          {Designing and developing a smart contract language and SDK for the Symbiont blockchain platform. Python was used heavily.}
        \resumeItem{Command Line Interface}
          {Contributing to the Symbiont CLI. It provides a convenient way to deploy and manage nodes. The CLI is written in Haskell.}
      \resumeItemListEnd

    \resumeSubheading
      {IBM Watson}{New York, NY}
      {Software Engineer}{Aug 2016 - Aug 2017}
      \resumeItemListStart
        \resumeItem{Conversational Agents}
          {Contributed to a service that provides businesses in a variety of
            industries a simple way to create virtual agents that can assist
            their customers. Worked on both the React front-end and the Go back-end.}
        \resumeItem{Notifications Service}
          {Created a notifications service that could be utilized by many services across IBM Watson to provide users with announcements and updates. The front-end is in Vue and the back-end in Go}
      \resumeItemListEnd

    \resumeSubheading
      {IBM Watson Internship}{New York, NY}
      {Software Engineer}{Jun 2015 - Aug 2015}
      \resumeItemListStart
        \resumeItem{Cognitive News Application}
          {Created a ``cognitive'' news aggregator and summarizer. Wrote both front-end and back-end code in React and Node.js respectively.}
      \resumeItemListEnd

    \resumeSubheading
      {The Office of Research at The Ohio State University}{Columbus, OH}
      {Software Engineer}{Aug 2013 - Aug 2014}
      \resumeItemListStart
        \resumeItem{CRUD Applications}
          {Worked on a variety of CRUD applications written in PHP for researchers across the university.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {The Ohio State University}{Columbus, OH}
    {Bachelors of Science in Computer Science \& Engineering;  GPA: 3.6}
    {Aug. 2012 -- May. 2016}
  \resumeSubheading
    {The Wellington School}{Columbus, OH}
    {GED;  GPA: 3.8}
    {Aug. 2008 -- May. 2012}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Baghodler}
      {A cryptocurrency portfolio tracker. It consumes many cryptocurrency
        exchange APIs to fetch trade history, normalizes the trades, and finally
        computes statistics from the trades. Written in Python.}
    \resumeSubItem{UDP Hole Punching}
      {Learned about the difficulties of creating and maintaining peer to peer
        [P2P] connections and how to solve them by reading a variety of relevant
        research papers and standards proposals. Created an experimental
        encrypted P2P chat application that uses the hole punching algorithm to
        create a direct connection between peers behind network address
        translator routers.}
    \resumeSubItem{Safe Payment Distributed App}
      {This payments system was created to learn more about distributed apps and
        the Ethereum platform. It allows users to securely purchase real world
        items with Ether. It ensures that both the purchaser receives the items
        she bought and that the seller receives the payment by holding Ether as collateral.}
  \resumeSubHeadingListEnd

%
%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}
     {Python, Javascript, Go, Haskell, C, PHP, SQL}
   \resumeSubItem{Front-end}
     {HTML, CSS3, SASS, Bootstrap, Webpack, React, Vue}
   \resumeSubItem{Database}
     {MySQL, SQLite, PostgreSQL, MongoDB}
   \resumeSubItem{Devops}
     {Docker, Kubernetes}
 \resumeSubHeadingListEnd

%-----------AWARDS-----------------
% \section{Awards}
% - The Ohio State University Trustees Scholarship (2012 - 2016)

% - The Ohio State University Honors Program (2012 - 2016)

% - The Wellington School Merit Scholarship (2008 - 2012)

%-------------------------------------------
\end{document}
